RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2014-12-31 manuscripts/manuscript.Rmd
Reorganizing RNeXML package description outline.

## Reading and writing phylogenies and character data

Conceptually, a NeXML document has the following components: (1)
phylogeny data, (2) character or trait data in matrix form, (3)
operational taxonomic units (OTUs), and (4) metadata. When reading and
writing NeXML, `RNeXML` aims to map these to and from, respectively,
their most natural representations in R. These are the `phylo` and
`multiPhylo` objects from the `ape` package [@Paradis_2004] for
phylogenies, and R's native `data.frame` list structure for character
matrices.

@@

The `nexml` object type is a representation of the NeXML
document contents, and therefore holds phylogenetic trees as well as 
character or trait matrices, and all metadata. This is similar in
design to the classes in the `phylobase` package, which contain 
trees and traits but hold only limited metadata [@phylobase], but
different from R object types such as `ape::phylo` (the `phylo` class
in the `ape` package [@Paradis_2004]), which represents trees alone.

@@

>>>>

## Representation of NeXML documents in R

Conceptually, a NeXML document has the following components: (1)
phylogeny data, (2) character or trait data in matrix form, (3)
operational taxonomic units (OTUs), and (4) metadata. `RNeXML` defines
the `nexml` object type, which is a representation of the NeXML
document contents. It therefore holds phylogenetic trees as well as
character or trait matrices, and all metadata. This is similar in
design to the classes in the `phylobase` package, which contain trees
and traits but hold only limited metadata [@phylobase], but different
from R object types such as `ape::phylo` (the `phylo` class in the
`ape` package [@Paradis_2004]), which represents trees alone.

When reading and writing NeXML documents, `RNeXML` aims to map their
components to and from, respectively, their most natural
representations in R. Hence, the types of objects accepted or returned
by the package's methods are the `phylo` and `multiPhylo` objects from
the `ape` package [@Paradis_2004] for phylogenies, and R's native
`data.frame` list structure for character matrices.

## Reading phylogenies and character data

@@

@@

## Writing phylogenies and character data
